---
title: "MrMarket_test_script"
author: "Piet"
date: "7/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Thesis: Do market ineffiencies happen more often at public companies, when private Investors hold a big stake in the company. In other terms, does the private investor ownership corelate with market ineffincies and is there a causal relationship between these two components?

Variables: 
1. Percentage of privately held ownership in a public traded company
2. Market Inefficiencies 

Because the second variable is quiet abstract I will go on and explain a bit more in detail what this study means by that. Inefficient means that a company's public valuation in form of the market capitalization does not reflect current informations about this specific company. In this case the company is either overvalued or undervalued. 
 
 
 
 GETTING DATA
 
 1. Variable: Percentage of privately owned stock in a given company 
```{r}
install.packages('quantmod')
library(quantmod)
library(rvest)
url <- "https://en.wikipedia.org/wiki/List_of_S%26P_500_companies"
SP500 <- url %>%
  html() %>%
  html_nodes(xpath='//*[@id="mw-content-text"]/div/table[1]') %>%
  html_table()
SP500 <- SP500[[1]]


spx <- getSymbols(Symbols = SP500[[1]], src = 'yahoo')


```
 
 